Tropopause Evolution in a Rapidly Intensifying Tropical Cyclone: A Static Stability Budget Analysis

### 2017-11-19 paper.tex
Added captions for Figs. 5-8.

\abstract{Enter the text of your abstract here.}

@@

%FIGURE 5%
\begin{figure*}[ht]
\centerline{\includegraphics[width=39pc]{figures/fig05_h000-h024-budgetterms.png}}
\caption{}
\label{fig:00-24}
\end{figure*}

%FIGURE 6%
\begin{figure*}[ht]
\centerline{\includegraphics[width=39pc]{figures/fig06_h024-h048-budgetterms.png}}
\caption{}
\label{fig:24-48}
\end{figure*}

%FIGURE 7%
\begin{figure*}[ht]
\centerline{\includegraphics[width=39pc]{figures/fig07_h048-h072-budgetterms.png}}
\caption{}
\label{fig:48-72}
\end{figure*}

%FIGURE 8%
\begin{figure*}[ht]
\centerline{\includegraphics[width=39pc]{figures/fig08_h072-h096-budgetterms.png}}
\caption{}
\label{fig:72-96}
\end{figure*}

>>>>

\abstract{We have some cool results!}

@@

%FIGURE 5%
\begin{figure*}[ht]
\centerline{\includegraphics[width=39pc]{figures/fig05_h000-h024-budgetterms.png}}
\caption{(a) Total change in N\textsuperscript{2} over the 0-24-hour period (10\textsuperscript{-4} s\textsuperscript{-2} (24 hr)\textsuperscript{-1}) and the contributions to that change from (b) the sum of horizontal and vertical advection, (c) vertical turbulence, and (d) the sum of longwave and shortwave radiation.}
\label{fig:stab-00-24}
\end{figure*}

%FIGURE 6%
\begin{figure*}[ht]
\centerline{\includegraphics[width=39pc]{figures/fig06_h024-h048-budgetterms.png}}
\caption{As in Fig.~\ref{fig:stab-00-24}, but for the 24-48-hour period.}
\label{fig:stab-24-48}
\end{figure*}

%FIGURE 7%
\begin{figure*}[ht]
\centerline{\includegraphics[width=33pc]{figures/fig07_h048-h072-budgetterms.png}}
\caption{(a) Total change in N\textsuperscript{2} over the 48-72-hour period (10\textsuperscript{-4} s\textsuperscript{-2} (24 hr)\textsuperscript{-1}) and the contributions to that change from (b) the sum of horizontal and vertical advection, (c) vertical turbulence, (d) the sum of longwave and shortwave radiation, (e) the sum of horizontal advection, vertical advection, and vertical turublence, and (f) the sum of horizontal advection, vertical advection, vertical turbulence, and longwave and shortwave radiation.}
\label{fig:stab-48-72}
\end{figure*}

%FIGURE 8%
\begin{figure*}[ht]
\centerline{\includegraphics[width=33pc]{figures/fig08_h072-h096-budgetterms.png}}
\caption{As in Fig.~\ref{fig:stab-48-72}, but for the 72-96-hour period.}
\label{fig:stab-72-96}
\end{figure*}
